---
output:
  pdf_document:
    toc: false
    keep_tex: true
    includes:
       in_header: codecheck-preamble.sty
    latex_engine: xelatex
---

```{r rsetup,eval=TRUE,include=FALSE}
require("codecheck")
require("knitr")
require("rprojroot")
require("yaml")
require("xtable")
require("tibble")
require("readr")
options(width = 60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df = copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path = FALSE,
                                  overwrite = FALSE)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```

# Summary

The codecheck was undertaken as part of a workshop at TU Delft on 18th
September 2023.  The codecheck was undertaken with the first author
observing and able to help fix issues.  This meant that the codecheck
was fairly quick and any issues were resolved fairly quickly.

We identified Figure 3 as the key figure to reproduce.  The other
results figures (particular 5 and 6) required significantly longer
computation times and so were not attempted.

During the codecheck, a hidden dependency was found.  The code
requires the Signal Processing Toolbox.  This should be documented in
the front page.

We found two problems with the code base, both presumably because the
code was developed on Windows, whereas the code was checked on a Mac.
First, path separators needed changing from '\\' to '/'.  Second, there
was an issue with some filenames having trailing spaces.  This was
fixed by changing the code to work with cell arrays rather than
vectors of characters.

With these fixes, the code was confirmed to work and Figure 3 could be
replicated.  This took under 2 hours, including all installations.


Once the code ran, I selected the six figures corresponding to the six
panels in Figure 3 and took a screenshot.  Scientifically, the results
are the same, although some visual differences are clearly seen
(e.g. y axis has been edited).  It was clear that there has been some
post-processing of the figures before publication, as was confirmed by
the author.

# CODECHECKER notes

The code was written in Matlab, with appropriate licence information.
There were three external dependencies required, which were
clearly described.  Installation of these extra software packages took
about 20 minutes.


I used MATLAB2023b on a mac to perform the check.  Once running, the
code took about 5 minutes to generate the key results.

To run the code, I needed to run the script "PlotResults.m".  This
then asked for three parameters, to which I selected "FLX 2kg", "100
Hz", "100 Hz".

As well as reproducing Figure 3, we were able to reproduce one row of
Table 1, "Flexion +" (Task 4).  These numbers were output to the terminal when
the code was run.  This output was:

```{verbatim}
Task considered: FLX_2kg
Considering RMR results at 100 Hz (with GH constraint)
Considering RMR results at 100 Hz (without GH constraint)
Considering CMC results
Warning: Integer operands are required for colon operator when used as index. 
> In EMG_CMC_RMR_plot (line 55)
In PlotResults (line 334)
 
MAE_flx2kg
    {'Trapezius, scapula middle'}

CMC:          0.03 [MAE] ,0.97 [xcorr]
RMR (GH):     0.04 [MAE] ,0.94 [xcorr]
RMR (no GH):  0.04 [MAE] ,0.94 [xcorr]

 
Warning: Integer operands are required for colon operator when used as index. 
> In EMG_CMC_RMR_plot (line 55)
In PlotResults (line 334)
 
MAE_flx2kg
    {'Trapezius, scapula superior'}

CMC:          0.06 [MAE] ,0.94 [xcorr]
RMR (GH):     0.08 [MAE] ,0.92 [xcorr]
RMR (no GH):  0.08 [MAE] ,0.92 [xcorr]

 
Warning: Integer operands are required for colon operator when used as index. 
> In EMG_CMC_RMR_plot (line 55)
In PlotResults (line 334)
 
MAE_flx2kg
    {'Trapezius, scapula inferior'}

CMC:          0.02 [MAE] ,0.94 [xcorr]
RMR (GH):     0.02 [MAE] ,0.9 [xcorr]
RMR (no GH):  0.02 [MAE] ,0.9 [xcorr]

 
Warning: Integer operands are required for colon operator when used as index. 
> In EMG_CMC_RMR_plot (line 55)
In PlotResults (line 334)
 
MAE_flx2kg
    {'Deltoid anterior'}

CMC:          0.05 [MAE] ,0.96 [xcorr]
RMR (GH):     0.05 [MAE] ,0.94 [xcorr]
RMR (no GH):  0.04 [MAE] ,0.95 [xcorr]

 
Warning: Integer operands are required for colon operator when used as index. 
> In EMG_CMC_RMR_plot (line 55)
In PlotResults (line 334)
 
MAE_flx2kg
    {'Deltoid posterior'}

CMC:          0.06 [MAE] ,0.44 [xcorr]
RMR (GH):     0.07 [MAE] ,0.14 [xcorr]
RMR (no GH):  0.07 [MAE] ,0.16 [xcorr]

 
Warning: Integer operands are required for colon operator when used as index. 
> In EMG_CMC_RMR_plot (line 55)
In PlotResults (line 334)
 
MAE_flx2kg
    {'Deltoid middle'}

CMC:          0.06 [MAE] ,0.94 [xcorr]
RMR (GH):     0.04 [MAE] ,0.97 [xcorr]
RMR (no GH):  0.05 [MAE] ,0.95 [xcorr]

 
Warning: Integer operands are required for colon operator when used as index. 
> In EMG_CMC_RMR_plot (line 55)
In PlotResults (line 334)
 
MAE_flx2kg
    {'Pectoralis major clavical'}

CMC:          0.04 [MAE] ,0.94 [xcorr]
RMR (GH):     0.04 [MAE] ,0.88 [xcorr]
RMR (no GH):  0.02 [MAE] ,0.91 [xcorr]

 
Warning: Integer operands are required for colon operator when used as index. 
> In EMG_CMC_RMR_plot (line 55)
In PlotResults (line 334)
 
MAE_flx2kg
    {'Serratus anterior'}

CMC:          0.06 [MAE] ,0.93 [xcorr]
RMR (GH):     0.06 [MAE] ,0.92 [xcorr]
RMR (no GH):  0.06 [MAE] ,0.92 [xcorr]

 
Warning: Integer operands are required for colon operator when used as index. 
> In EMG_CMC_RMR_plot (line 55)
In PlotResults (line 334)
 
MAE_flx2kg
    {'Infraspinatus (Superior)'}

CMC:          0.02 [MAE] ,0.93 [xcorr]
RMR (GH):     0.02 [MAE] ,0.73 [xcorr]
RMR (no GH):  0.04 [MAE] ,0.56 [xcorr]

 
Warning: Integer operands are required for colon operator when used as index. 
> In EMG_CMC_RMR_plot (line 55)
In PlotResults (line 334)
 
MAE_flx2kg
    {'Latissimus Dorsi (Medialis)'}

CMC:          0.15 [MAE] ,0.84 [xcorr]
RMR (GH):     0.16 [MAE] ,0.52 [xcorr]
RMR (no GH):  0.16 [MAE] ,0.55 [xcorr]

 
Warning: Integer operands are required for colon operator when used as index. 
> In EMG_CMC_RMR_plot (line 55)
In PlotResults (line 334)
 
MAE_flx2kg
    {'Teres major'}

CMC:          0.09 [MAE] ,0.4 [xcorr]
RMR (GH):     0.11 [MAE] ,0.06 [xcorr]
RMR (no GH):  0.1 [MAE] ,0.05 [xcorr]

 
>>
```


## Recommendations


- Document the "Signal Processing toolbox" dependency.

- Consider portable code that works across operating systems,
particularly with respect to directory separators.

- Consider whether the external data "Thoracoscapular" could be
included in your repository.  There are pros and cons of copying data
into your repository versus asking users for an extra installation.

- Consider writing short functions that include the key parameters
needed to generate results, rather than needing an interactive GUI.

- The results to generate Table 1 could be stored to a file, rather
  than simply printed to the terminal.
  

\clearpage

# Manifest files

```{r, echo=FALSE, results="asis", width=100}
for(i in c(1:nrow(manifest_df))) {
  path <- manifest_df[i,"dest"]
  if(stringr::str_ends(path, "(png|pdf|jpg|jpeg)")) {
    # include graphics with knitr has to happen at top level in chunks, see https://github.com/yihui/knitr/issues/1260
    # see also https://stackoverflow.com/questions/51268623/insert-images-using-knitrinclude-graphics-in-a-for-loop
    # knitr::include_graphics(manifest_df[1, "dest"], error = TRUE)
    # Therefore, generate Markdown code here:
    cat("## ", basename(path), "\n\n")
    cat("**Comment:** ", manifest_df[i,"comment"], "\n\n")
    cat(paste0("![", "Test ", "](", path, ")\n"))
  } else if (stringr::str_ends(path, "(Rout|txt)")) {
    cat("## ", basename(path), "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    cat(readLines(path), sep = "\n")
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "csv")) {
    cat("## ", basename(path), "\n\n", "Summary statistics of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(skimr::skim(read.csv(path)))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else {
    cat("## ", basename(path), "\n\n")
    cat("Cannot inlcude output file as figure.")
  }
  
  cat("\\clearpage \n\n")
}
```

\clearpage

## Acknowledgements

Thanks to Italo Belli for volunteering his work to be checked.


# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
